Distribution-oblivious Programming with Dish

### 2019-10-03 pldi/draft.tex
Update intro

The key insight behind our work is that \unix pipelines already provide most of the information for distributing a computation.
Indeed, the primary reason behind $p_1$'s succinctness is that the pipeline is a domain-specific language for describing operations over streams.
Primitives 
\sys enables \emph{distribution-oblivious programming}: 
  multi-order of magnitude speedups with correctness guarantees and without any developer effort.

>>>>

The key insight behind our work is that \unix pipelines already provide most of the information for distributing a computation.
Commands

Indeed, the primary reason behind $p_1$'s succinctness is that the pipeline is a domain-specific language for describing operations over streams.
Key elements of \unix are the ability to compose programs written in different languages, the abstraction of a file system as a set of resident streams, a small but extensible library of commands, and the ability to resolve names within a global context.
Under the hood, the \unix kernel buffers results, synchronizes processing stages, and generally orchestrates the computation.

Primitives 
\sys enables \emph{distribution-oblivious programming}: 
  multi-order of magnitude speedups with correctness guarantees and without any developer effort.
